Instructions for \confname{} Proceedings

### 2019-05-15 papers/EMNLP2019/analysis.tex
corrects tex bug; modifies 1 sentence in intro

In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object. Second, we will uses the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
\begin{figure}[t]
	\centering
	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vandertwart \& Snodgrass) \label{fig:picture_naming}}}
\end{figure}

>>>>

In this section, we investigate to what extent names annotated in VisualGenome and elicited in ManyNames can be considered canonical, i.e. to what extent speakers agree in their naming choices.
Whereas traditional picture naming studies typically use a prototypical image per category (see Figure~\ref{fig:picture_naming}) and, hence, are mostly interested in the agreement on concept or category-level, we carry out an anaylsis on two different levels: First, we will look at instances and see to what extent names overlap for the same object. Second, we will uses the existing annotation of names in VisualGenome to analyze agreement on the level of categories.
\begin{figure}[t]
	\centering
	\includegraphics[scale=.5]{figures/snodgrass_vanderwart_cake_042.png}
	\caption{Example of a picture of \textsl{cake} used in traditional picture naming studies (REF to Vanderwart \& Snodgrass) \label{fig:picture_naming}}
\end{figure}
